---
title: "YoghurtCase"
author: "Team 4"
date: "2/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

############ SQL CODE ############

# Load the dataset retailer1
use retailer1;

# Show all the tables we can leverage in the dataset
show tables; 

# Extract data with classification as GREEK, flavors, and sum of sales of each flavor from itemsAttributes table and storeItemSales table 
select Class, Flavor1, sum(Sales) from itemsAttributes join storeItemSales on itemsAttributes.`Item.Num` = storeItemSales.`Item.Num`
where Class = "GREEK"
group by Flavor1; 

# Extract data with classification as REGULAR, flavors, and sum of sales of each flavor from itemsAttributes table and storeItemSales table
select Class, Flavor1, sum(Sales) from itemsAttributes join storeItemSales on itemsAttributes.`Item.Num` = storeItemSales.`Item.Num`
where Class = "REGULAR"
group by Flavor1;

# Time serise analysis: Sales of Greek yogurt increased the most in 2011
select Week_Ending, Class, Flavor1, sum(Sales) from itemsAttributes join storeItemSales on itemsAttributes.`Item.Num` = storeItemSales.`Item.Num`
where Class = "GREEK"
group by Flavor1, Week_Ending;

# Unit analysis: Sum of units of each flavor
select Class, Flavor1, sum(Units) from itemsAttributes join storeItemSales
on itemsAttributes.`Item.Num` = storeItemSales.`Item.Num`
where Class = 'GREEK'
group by Flavor1;

#After extracting and saving data in a .csv file: For Greek Yoghurt - Greekdata.csv and for Regular Yoghurt - RegularData.cs

install.packages("knitr")
library("knitr")
install.packages("ggplot2")
library("ggplot2")

```{r QUESTION1, echo=TRUE}
#Loading the relevant data
library(readr)
GreekData <- read.csv("Lovett/GreekData.csv")


#Renaming columns appropriately
colnames(GreekData)[1] <- "Class"
colnames(GreekData)[2] <- "Flavor"
colnames(GreekData)[3] <- "Sales"

#Finding flavors by percentage sold
total <- sum(GreekData$Sales)
GreekData$percentages <- (GreekData$Sales/total)*100

#Plotting bar plot for visualisation
bp <- ggplot(GreekData, aes(x=reorder(Flavor, -percentages), y=percentages, fill=Flavor))+
  geom_bar(width = 1, stat = "identity")
bp
```


```{r QUESTION 2, echo=TRUE}
#Loading the relevant data
library(readr)
RegularData <- read.csv("Lovett/RegularData.csv")


#Renaming columns appropriately
colnames(RegularData)[1] <- "Class"
colnames(RegularData)[2] <- "Flavor"
colnames(RegularData)[3] <- "Sales"

#Finding flavors by percentage sold
total <- sum(RegularData$Sales)
RegularData$percentages <- (RegularData$Sales/total)*100

#Plotting bar plot for visualisation
bp <- ggplot(RegularData, aes(x=reorder(Flavor, -percentages), y=percentages, fill=Flavor))+
  geom_bar(width = 1, stat = "identity")
bp

```
```{r Top 10 Regular , echo=TRUE}

#Better visualisation of top 10 flavors 
RegularData.Top <- RegularData[order(-RegularData$percentages),]
RegularData.Top <- RegularData.Top[1:10,]
bp <- ggplot(RegularData.Top, aes(x=reorder(Flavor, -percentages), y=percentages, fill=Flavor))+
  geom_bar(width = 1, stat = "identity")
bp
```

```{r QUESTION 3, echo=TRUE}

df <- read.csv("~/Desktop/design/hm2/survResponses.csv")
Greek = df[df$Q2_1 == '100', ] #we only want to know the popular flavors among greek yogurt. 
flavor = Greek[,15:37]

df2 <- data.frame(
                  often=integer(), 
                 sometime=integer(), 
                 never = integer(),
                 stringsAsFactors=FALSE) 

par(mfrow=c(4,6));
for(j in 1:23){
  x =flavor[,j]
  if(is.numeric(x)){
    hist(x,main=names(flavor)[j])
   df2[j,] = table(x)
  } else {
    plot(x,main=names(flavor)[j])
    df2[j,] = table(x)
  }
}

df2[order(-df2$often),]

```
From the chart above, we can find that blueberry,respberry and strawberry are the most famous flavor.Chai and maple are the Least popular flavors.

```{r QUESTION 4, echo=TRUE}
## TURF analysis #######
##### TURF function ######
measReach = function(data){
  if(is.null(dim(data))){ #if data is a vector
    ret = sum(data>0,na.rm=TRUE)/length(data)
  } else if(ncol(data)==1){ #if data has only one column
    ret = sum(data>0,na.rm=TRUE)/length(data)
  }
  else { #if data has multiple columns
    ret = sum(apply(data>0,1,any),na.rm=TRUE)/nrow(data)
  }
}

evalNext = function(nextSet,set,data,measure=measReach){
  vals = numeric(length(nextSet)) #set up storage for return value
  for(k in 1:length(nextSet)){ #loop over the options in nextSet
    if(length(set)==0){         #if no existing options
      vals[k] = measure(data[,nextSet[k]]) 
    } else {                    #if existing options
      vals[k] = measure(data[,c(set,nextSet[k])])
    }
  }
  vals
}

evalFull = function(fullSet,data,origSet=numeric(0),measure=measReach){
  curSet = origSet; #the current set of included options
  remSet = fullSet[!(fullSet%in%origSet)]; #the remaining set of options to consider
  K = length(remSet)
  optVals = numeric(K); #create storage for the optimal values (optVals)
  ordSet = numeric(K); #create storage for ordered set
  for(i in 1:K){          #loop over the remaining set consider
    tmpVals = evalNext(remSet,curSet,data,measure); #calculate vector of next evaluations
    k = which.max(tmpVals) #pick the option that gives max measure, note will pick first case if a tie!
    optVals[i] = tmpVals[k] #add optimal value
    ordSet[i] = remSet[k]   #add index of option that creates optimal value
    curSet = c(curSet,ordSet[i]); #add optimal next option to current set
    remSet = remSet[-k];          #delete optimal next option from remaining set
  }
  #creaets a "TURF object" containing ordSet, optVals, origSet, origVal, measure, and pnames
   turf = list(ordSet=ordSet,optVals=optVals,origSet=origSet,origVal=measure(data[,origSet]),measure=measure,pnames=colnames(data))
  class(turf)="TURF" #makes the list into a TURF object so that can call plot.TURF
  turf  #return turf
}
#creates ggplot barplot for a turf object
plot.TURF=function(turf,...){
  if(class(turf)!="TURF"){
    cat("Object not a turf.")
  } else {
    df = with(turf,data.frame(vals = c(origVal,optVals),titles=paste(0:length(ordSet),c("Original",pnames[ordSet]),sep=":")))
    #with(turf,barplot(c(origVal,optVals),names.arg=c("Original",pnames[ordSet])))
    dodge = position_dodge(width=.75); ##to form constant dimensions positioning for all geom's
    gp = ggplot(df,aes(y=vals,x=titles))
    gp + geom_bar(position=dodge,stat="identity",col=1,fill=4,width=.75)
  }
}

####### clean data ######
res <- read.csv("~/Desktop/design/hm2/survResponses.csv")
for (i in 15:37){
    res[,i][which(res[,i] == '2')] <- 'a'
    res[,i][which(res[,i] == '1')] <- 'a'
    res[,i][which(res[,i] == '0')] <- 'b'
    res[,i][which(res[,i] == 'a')] <- '0'
    res[,i][which(res[,i] == 'b')] <- '1'
    
}

####### compelete responses #####
res = res[res$V10 == 1,]
##### less than 30 mins and more than 1 mins responses #####
res$time = difftime(res$V9,res$V8,units=c('mins'))
resshorttime = res[res$time < 30 ,]
resshorttime = resshorttime[resshorttime$time > 1 ,]
##### people who often buy greek yorgurt #######
greekshorttime = resshorttime[resshorttime$Q2_1 >= 50,]

##### greek yogurt flavors ######
Purch3 =greekshorttime[,15:37]
###### delete  NA rows which only contain NAs #####
Purch4<-Purch3[-which(apply(Purch3,1,function(x) all(is.na(x)))),]
##### set other NAs to 0 #######
Purch4[is.na(Purch4)]= 0
##### rename the flavors ########
names(Purch4)=c("Almond", "Banana", "Black Cherry", "Blueberry", "Caramel", "Chai", "Chocolate", "Cinnamon", "Coconut", "Honey", "Key Lime Pie", "Lemon", "Mango", "Mapel", "Peach", "Pineapple", "Plain", "Pomegranate", "Raspberry", "Strawberry", "StrawBan", "Vanilla", "VaniBan")
##### TURF #########
turf2 = evalFull(c(1:23),Purch4,c(4,20,15,22,17,10))
plot(turf2)

```
From TURF analysis, we can find that for all type of yogurt, it is best to launch pineapple, black cherry and lemon flavor. While for only Greek yogurt, it is best to launch black cherry and lemon flavor.

# what's more, we further did a family size analysis to determine what size of yogurt combo the brand should launch using the surveys data. we found out that in most occasions, the families sizes are 4-5, so maybe besides separate packing, the brand can also launch the 4-5 packing combo.

select Flavor1, sum(Sales),FSBin
from survItemSales s join itemsAttributes i on s.`Item.Num` = i.`Item.Num` join 
hshldDemograph h on s.`Household.Num` = h.`Household.Num`
where Flavor1 = 'raspberry' or Flavor1 = 'black cherry' or Flavor1 = 'pineapple' or Flavor1 = 'lemon'
group by FSBin, Flavor1;

